Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-18 Markdown Documents/Manuscript.Rmd

```{r include=FALSE, cache=TRUE}
library(tidyverse)
library(lme4)
library(rstan)
Data<-read_csv("Data/MergedDataComplete.csv")[,-1]
Data$date<-zoo::as.yearmon(paste0(Data$Month,Data$Year),"%m%Y")
Data<-Data%>%group_by(UnitCode,Month)%>%mutate(ARVis = lag(RecreationVisits) )
Data$VisChange<-(Data$RecreationVisits-Data$ARVis)/Data$ARVis
Data<-na.omit(Data)

>>>>

```{r include=FALSE, cache=TRUE}
library(tidyverse)
library(lme4)
library(rstan)
Data<-read_csv("~/SmokeProject/Data/MergedDataComplete.csv")[,-1]
Data$date<-zoo::as.yearmon(paste0(Data$Month,Data$Year),"%m%Y")
Data<-Data%>%group_by(UnitCode,Month)%>%mutate(ARVis = lag(RecreationVisits) )
Data$VisChange<-(Data$RecreationVisits-Data$ARVis)/Data$ARVis
Data<-na.omit(Data)
